---
title: "p8105_hw5_yj2686"
author: "Yiqun Jin"
date: "11/15/2021"
output: github_document
---

```{r setup}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

For this problem, we are interested in data gathered and made public by _The Washington Post_ on homicides in 50 large U.S. cities. The code chunk below imports and clans the data.

```{r}
homicide_df = read.csv("./data/homicide-data.csv", na = c("","Unknown")) %>% 
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore, MD.

```{r}
baltimore_df = homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = prop.test(
  x = baltimore_summary %>% pull(unsolved), 
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

Let's try to iterate across states:

First off, write a function and test it on a few sample cities.

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = prop.test(
    x = city_summary %>% pull(unsolved), 
    n = city_summary %>% pull(n))
  
  return(city_test)
}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Now, let's iterate across all cities.

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```

Try to make a plot showing estimates and confidence intervals

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```


## Problem 2


```{r}
tibble(files = list.files("./data/zip_data/"))
```


## Problem 3
