---
title: "p8105_hw5_yj2686"
author: "Yiqun Jin"
date: "11/15/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

For this problem, we are interested in data gathered and made public by _The Washington Post_ on more than 52,000 criminal homicides over the past decade in 50 large U.S. cities. The data included the location of the killing, whether an arrest was made and basic demographic information about each victim. The code chunk below imports and clans the data.

```{r}
homicide_df = read.csv("./data/homicide-data.csv", na = c("","Unknown")) %>% 
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore, MD.

```{r}
baltimore_df = homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = prop.test(
  x = baltimore_summary %>% pull(unsolved), 
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

Iterate across states:

First, Write a function.

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = prop.test(
    x = city_summary %>% pull(unsolved), 
    n = city_summary %>% pull(n))
  
  return(city_test)
}
```

Second, iterate across all cities.

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```

Make a plot showing estimates and confidence intervals for each cities and organize cities according to the proportion of unsolved homicides.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(title = "Estimates of Proportions of Homicides 
       that are Unsolved and Confidence Interval for Each Cities") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
        plot.title = element_text(hjust = 0.5))
```

## Problem 2

Create a tidy dataframe containing data from all participants

```{r}
zip_df = tibble(files = list.files("./data/zip_data/")) %>% 
  mutate(
    path = str_c("./data/zip_data/",files),
    result = map(path, read.csv)
  ) %>% 
  unnest(result) %>% 
  separate(
    files, c("arm","subject_id","format")
  ) %>% 
  select(-format, -path) %>% 
  mutate(
    arm = ifelse(arm == "con", "control", "experimental")
  ) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "result"
  )
```

Make a spaghetti plot showing observations on each subject over time

```{r}
zip_df %>% 
  ggplot(aes(x = week, y = result, color = subject_id)) +
  facet_grid(. ~ arm) +
  geom_line(aes(group = subject_id)) +
  labs(title = "Spaghetti Plot of Observations on 
       Control Arm and Experimental Arm over 8 Weeks",
       y = "Observation values") +
  theme(plot.title = element_text(hjust = 0.5))
```

According to the spaghetti plot above, the observations of experimental arm show a increasing trend over 8 weeks. As for the control arm, there are some fluctuations over time but the observations do not show any obvious trend. Except week 1, the observations of experimental arm do not have values below 0. However, several observations of control arm have values below 0.

## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function.

```{r}
fill_in_missing = function(vector) {
  
  if (is.numeric(vector)) {
    vector[is.na(vector)] = mean(vector,na.rm = T)
  }
  
  else if (is.character(vector)) {
    vector[is.na(vector)] = "virginica"
  }
  return(vector)
}
```

Apply the function to iris dataset 

```{r}
iris_with_missing = map(iris_with_missing, fill_in_missing) 
iris_with_missing %>% as_tibble() %>% knitr::kable()
```

